\documentclass[a4paper,10pt]{article}
\usepackage[left=0.7in, right=0.7in, top=0.7in, bottom=0.7in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multicol} % for columns
\usepackage{fontawesome} % for icons
\setlength{\parindent}{0pt}
\renewcommand{\familydefault}{\sfdefault}

% Define consistent spacing for full-width section headers
\newcommand{\sectionheader}[1]{%
    \textbf{\LARGE #1}\\[-0.5ex]
    \textbf{\LARGE \underline{\hspace{\textwidth}}}\\[2ex]
}

% Define consistent spacing for column section headers
\newcommand{\columnsectionheader}[1]{%
    \textbf{\LARGE #1}\\[-0.5ex]
    \textbf{\LARGE \underline{\hspace{0.45\textwidth}}}\\[2ex]
}

% Define company header style
\newcommand{\companyheader}[2]{%
    \vspace{1ex}
    \textbf{\large #1} \hfill \faCalendar \, #2
    \vspace{0.5ex}
}

\begin{document}

\begin{center}
    \textbf{\LARGE Ajay Nehra} \\
    \vspace{1mm}
    \href{mailto:nehraa.2014@iitkalumni.org}{nehraa.2014@iitkalumni.org} \hspace{5mm} (+91)-9997272281
\end{center}

\vspace{4mm}

% Summary content without header
Data scientist with 9+ years of experience in designing, building, and deploying scalable, data-driven solutions across industries. Highly skilled in Python, R, SQL, and cloud technologies. Excellent problem-solving abilities, with a robust understanding of statistics and machine learning.

\vspace{4mm}

\begin{multicols}{2}

% Education Section
\columnsectionheader{Education}
\textbf{B.Tech in Civil Engineering} \\
\textbf{IIT Kanpur} \\
\faCalendar \, Jul 2010 - May 2014 \\
\textbf{CGPA:} 7.1

\columnbreak

% Skills Section
\columnsectionheader{Skills}
\textbf{Programming Languages:} Python, R, SQL, C \\
\textbf{Cloud Technologies:} Azure, Databricks \\
\textbf{Data Visualization:} Tableau, R Shiny, Power BI \\
\textbf{MLOps \& Version Control:} Kedro, Git, Docker

\end{multicols}

\vspace{4mm}

% Work Experience Section
\sectionheader{Work Experience}

% McKinsey
\companyheader{Specialist - Data Sciences @ McKinsey \& Company}{Nov 2019 - Present}
\begin{itemize}
    \item Developed a data science pipeline by integrating a linear mixed-effects model (LMM) to optimize car sales incentives, leading to a 15\% reduction in budget while increasing sales volume by 10\% across key markets.
    \item Delivered end-to-end solutions for revenue growth management and promotion planning for CPG clients, achieving a 20\% increase in profitability through econometric modeling and machine learning.
    \item Led cross-functional team collaborations to implement big data pipelines, enhancing model deployment efficiency and reducing processing time by 40\%.
    \item Conducted R\&D to identify growth opportunities, leveraging machine learning to optimize promotional spends and boost revenue by 25\% for retail clients.
\end{itemize}

% IND-Money
\companyheader{Machine Learning Engineer @ IND-Money}{May 2019 - Oct 2019}
\begin{itemize}
    \item Designed and developed ETL pipelines to integrate third-party vendor data, automating data ingestion for the IND-Money app, resulting in a 30\% reduction in processing latency.
\end{itemize}

% EY
\companyheader{Senior Consultant - Data Sciences @ EY (Ernst \& Young)}{Oct 2017 - May 2019}
\begin{itemize}
    \item Designed time-variant Expected Credit Loss (ECL) models under IFRS 9, building Probability of Default (PD) and Loss Given Default (LGD) models to ensure accurate risk forecasting across loan terms, aligning with regulatory requirements for major Gulf financial institutions.
    \item Automated ECL calculation pipelines, reducing manual effort by 60\% and improving reporting accuracy, enabling timely compliance with IFRS 9.
    \item Embedded governance workflows for regulatory audits and scenario analysis, establishing a robust, transparent compliance framework that reduced regulatory review time by 30\%.
\end{itemize}

% MasterCard Advisors
\companyheader{Data Scientist @ MasterCard Advisors}{Jan 2016 - Jun 2017}
\begin{itemize}
    \item Developed predictive models for banks and merchants, leveraging transactional data to optimize marketing spend and increase engagement.
    \item Utilized big data technologies (Spark, Hadoop) to handle high-volume data, enhancing processing efficiency for clients by 50\%.
\end{itemize}

% Fractal Analytics
\companyheader{Business Analyst @ Fractal Analytics}{Jul 2014 - Dec 2015}
\begin{itemize}
    \item Conducted marketing mix modeling using Log-Linear models to optimize client marketing investments, achieving a 10\% increase in ROI.
    \item Developed a custom R Shiny visualization tool to help CPG clients analyze growth drivers, enabling faster decision-making and 20\% more effective resource allocation.
\end{itemize}

\vspace{4mm}

% Achievements Section
\sectionheader{Achievements}
Academic: All India Rank 1771 in IIT JEE 2010 (top 0.4\%) and 2575 in AIEEE 2010 (top 0.3\%) \\
Innovation: Filed 6 patents on payment system technologies at Mastercard Advisors

\end{document}