\documentclass[a4paper,12pt]{article}

\usepackage[utf8]{inputenc}

\usepackage{enumitem}
\usepackage{geometry}
\usepackage{titlesec}

% Set page margins
\geometry{left=1cm,right=1cm,top=2cm,bottom=2cm}

% Define section formatting
\titleformat{\section}
{\normalfont\Large\bfseries}
{}{0em}{}

\begin{document}

% Header
\begin{center}
    \textbf{\Huge Ajay Nehra}
\end{center}

% Contact Information
\section*{Contact Information}
\begin{tabular}{@{}ll}
    \textbf{Phone:} (+91)-9997272281 & \textbf{Email:} nehraa.2014@iitkalumni.org \\
\end{tabular}

% Summary
\section*{Summary}
Data scientist with 7+ years of experience in development and deployment of data-driven solutions across industries. Highly skilled in Python, R, SQL, and cloud technologies (Databricks, Azure, and AWS). Strong analytical and critical thinking skills combined with a deep understanding of statistical modeling and machine learning algorithms.


% Education
\section*{Education}
\textbf{Indian Institute of Technology (IIT), Kanpur} \hfill \textnormal{Jul 2010 - May 2014} \\
Bachelor of Technology in Civil Engineering

% Work Experience
\section*{Work Experience}
\begin{itemize}[leftmargin=0.2cm, label={}]
    \item \textbf{McKinsey \& Company, Specialist-Data Sciences} \hfill \textnormal{Nov 2019 to Present}
    \begin{itemize}[leftmargin=0.5cm, label={\textbullet}]
        \item Leveraged machine learning algorithms to uncover price patterns and opportunities for revenue and profit optimization.
        \item Led the development and deployment of pricing models and profit optimization solutions for CPG clients.
        \item Collaborated with cross-functional teams to gather requirements, develop product features, and evaluate product performance.
    \end{itemize}
    
    \item \textbf{EY (Ernst \& Young), Senior Consultant-Data Sciences} \hfill \textnormal{Oct 2017 to May 2019}
    \begin{itemize}[leftmargin=0.5cm, label={\textbullet}]
        \item Deployed credit scoring models by implementing logistic regression, random forests, and gradient boosting to assess creditworthiness and enable informed lending decisions for banks in Dubai, Abu Dhabi, Kuwait, Qatar, and Bahrain.
        \item Created ETL pipelines to automate the regulatory requirements of banks and internal reporting.
    \end{itemize}
    
    \item \textbf{MasterCard Advisors, Data Scientist} \hfill \textnormal{Jan 2016 to Jun 2017}
    \begin{itemize}[leftmargin=0.5cm, label={\textbullet}]
        \item Developed data-driven solutions for banks and merchants by training machine learning models on transactional data.
        \item Leveraged big data technologies like (Spark \& Hadoop) to manage high volume and velocity of transactional data.
    \end{itemize}
    
    \item \textbf{Fractal Analytics, Business Analyst} \hfill \textnormal{Jul 2014 to Dec 2015}
    \begin{itemize}[leftmargin=0.5cm, label={\textbullet}]
        \item Conducted marketing mix modeling using Log-Linear model to assess the effectiveness of marketing events and channels.
    \end{itemize}
\end{itemize}

% Skills
\section*{Skills}
\begin{itemize}[leftmargin=0.2cm, label={}]
    \item \textbf{Programming Languages:} Python \& PySpark, R, SQL, C
    \item \textbf{Cloud Technologies:} Databricks, Azure, AWS
    \item \textbf{Core Engineering:} Probability \& Statistics, Linear Algebra, Numerical Methods for Computation
    \item \textbf{MLOps:} Git, Docker, Jenkins
    \item \textbf{Visualization:} Tableau, R Shiny
\end{itemize}

% Achievements
\section*{Achievements}
\begin{itemize}[leftmargin=0.2cm, label={}]
    \item All India Rank 1771 in IIT JEE 2010 (top 0.4\%) and 2575 in AIEEE 2010 (top 0.3\%)
    \item Filed 6 patents on payment systems technologies and solutions in Mastercard Advisors
\end{itemize}

\end{document}
