% Summary content without header
Senior Data Scientist with 9+ years of experience delivering scalable ML and econometric solutions across diverse industries. IIT Kanpur graduate with deep expertise in statistics, forecasting, and end-to-end model deployment.

% McKinsey
{\large Senior Data Scientist II} \\ 
\textbf{McKinsey \& Company} \\
\faCalendar \, Nov 2019 - Present \hfill \faMapMarker \, Gurgaon
\begin{itemize}[itemsep=1pt, topsep=0pt]
    \item Engineered a price optimization pipeline using linear mixed-effects models, boosting car sales volume by 7\% within budget and regulatory constraints.
    \item Delivered high-impact analytics products for CPG clients by combining econometric and ML techniques, driving a 10\% revenue uplift.
    \item Spearheaded cross-functional efforts to productionize ML workflows, cutting deployment time by 40\% and improving system reliability.
\end{itemize}

% IND-Money
{\large Machine Learning Engineer} \\
\textbf{INDMoney} \\
\faCalendar \, May 2019 - Oct 2019 \hfill \faMapMarker \, Gurgaon
\begin{itemize}[itemsep=1pt, topsep=0pt]
    \item Built a real-time expense classification engine using NER and supervised learning on SMS feeds, enabling smart categorization for personal finance users.
\end{itemize}

% EY
{\large Senior Consultant - Data Sciences} \\
\textbf{EY (Ernst \& Young)} \\
\faCalendar \, Oct 2017 - May 2019 \hfill \faMapMarker \, Dubai \& Mumbai
\begin{itemize}[itemsep=1pt, topsep=0pt]
    \item Designed and deployed IFRS 9-compliant ECL calculator using PD, LGD, and EAD models to automate risk provisioning.
    \item Converted TTC to PIT PD models for granular risk insights, improving credit decisioning and regulatory alignment.
    \item Automated multi-stage capital reporting, enhancing auditability and reducing manual compliance effort by 60\%.
\end{itemize}

% MasterCard Advisors
{\large Data Scientist} \\
\textbf{MasterCard Advisors} \\
\faCalendar \, Jan 2016 - Jun 2017 \hfill \faMapMarker \, Gurgaon
\begin{itemize}[itemsep=1pt, topsep=0pt]
    \item Formulated acquisition strategies via decision trees, boosting upsell and cross-sell rates by 10\%.
    \item Leveraged Spark/Hadoop to segment customers with k-Means clustering on billions of transactions (e.g., travelers, premium shoppers).
    \item Streamlined outreach targeting, reducing customer acquisition costs by 30\% through high-propensity scoring.
\end{itemize}

% Fractal Analytics
{\large Business Analyst} \\
\textbf{Fractal Analytics} \\
\faCalendar \, Jul 2014 - Dec 2015 \hfill \faMapMarker \, Gurgaon
\begin{itemize}[itemsep=1pt, topsep=0pt]
    \item Built marketing mix models to optimize spend, yielding an 8\% lift in campaign ROI.
    \item Created R Shiny dashboards for portfolio tracking and executive reporting across geographies.
\end{itemize}